Laziness in R

### 2019-02-03 report/report.Rmd
Fix summarization, visualization, report of execution time analysis
Add analysis steps for promise evaluation and nesting depth

>>>>

## Argument execution time

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_execution_time_by_parameter_class.png")
```

## Promise Evaluation

### Call Depth

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_call_depth.png")
```

```{r echo = FALSE}
show_table("argument_count_by_call_depth")
```

### Promise Depth

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_promise_depth.png")
```

```{r echo = FALSE}
show_table("argument_count_by_promise_depth")
```

### Nested Promise Depth

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_nested_promise_depth.png")
```

```{r echo = FALSE}
show_table("argument_count_by_nested_promise_depth")
```
